TTS OD by Purpose by Start Time/Day of Week

### 2024-11-18 data-raw/02-TTS16-Imp-Function-Trip-Length-Distribution.Rmd
Commit to move from Windows

Load packages:
```{r}
library(ggplot2)
library(dplyr)
library(MASS)

# install.packages("fitdistrplus")
# install.packages("logspline")
library(fitdistrplus)
library(logspline)

@@

>>>>

Load packages:
```{r}
library(dplyr) # A Grammar of Data Manipulation
library(fitdistrplus) # Help to Fit of a Parametric Distribution to Non-Censored or Censored Data
library(ggplot2) # Create Elegant Data Visualisations Using the Grammar of Graphics
library(logspline) # Routines for Logspline Density Estimation
library(MASS) # Support Functions and Datasets for Venables and Ripley's MASS

@@

<!--FILE NOT THERE!!-->

### 2024-11-18 data-raw/04-GGH4-Extract-OD-by-Purpose-Mode-Time-Day-from-Raw-Files (SFConflict paezha@mcmaster.ca 2024-01-20-14-51-34).Rmd
Commit to move from Windows

@@

-->

>>>>

Save to parquet for sharing:
```{r}
library(arrow)
# using compression
if (codec_is_available("gzip")) {
  tf <- tempfile(tmpdir = glue::glue(stringr::str_replace_all(here::here(), "/", "\\\\"),
                                     "\\data-raw\\TTS16-data-inputs\\OD-GGH4-by-Time-Day-Mode-Purpose\\"),
                 fileext = ".gz.parquet")
  write_parquet(od_ggh4_mode_purpose,
                tf, 
                compression = "gzip", 
                compression_level = 5)
}
```

Rename file:
```{r}
arrow_file <- list.files(path = glue::glue(here::here(), 
                             "/data-raw/TTS16-data-inputs/OD-GGH4-by-Time-Day-Mode-Purpose"),
           pattern = "^(.*)\\.gz.parquet$")
# arrow_file <- stringr::str_replace(arrow_file,
#                                    stringr::str_extract(arrow_file, "[^.]+"),
#                                    glue::glue(, ""))

file.rename(from = glue::glue(here::here(), 
                             "/data-raw/TTS16-data-inputs/OD-GGH4-by-Time-Day-Mode-Purpose/{arrow_file}"), 
            to = glue::glue(here::here(), 
                             "/data-raw/TTS16-data-inputs/OD-GGH4-by-Time-Day-Mode-Purpose/od_ggh4_mode_purpose.gz.parquet"))
```

Remove data object:
```{r}
rm(od_ggh4_mode_purpose)
```

Check that parquet file can be read:
```{r}
od_ggh4_mode_purpose <- read_parquet(glue::glue(here::here(), 
                             "/data-raw/TTS16-data-inputs/OD-GGH4-by-Time-Day-Mode-Purpose/od_ggh4_mode_purpose.gz.parquet"),
             as_data_frame = FALSE)
```

@@
